Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-03-24 ms/ms08_figures.tex
ENH

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 1: Histogram of percentage of explained of GWAS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\caption{}
\label{fig:region_gwas_egenes_tissues}
%
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 2: ucsc screenshots
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!ht]
    \centering

    \begin{subfigure}[]{0.99\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{fig/ucsc_gwas2eqtl_il4_bcell_help.png}
    \end{subfigure}

    \begin{subfigure}[]{0.99\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{fig/ucsc_gwas2eqtl_il4_monocyte.png}
    \end{subfigure}

    \begin{subfigure}[]{0.99\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{fig/ucsc_gwas2eqtl_il4_frontalcortex.png}
    \end{subfigure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 3: Trait distance matrix
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!ht]
    %
    \centering
    %
    \includegraphics[width=\textwidth]{\floatRelativePath/plthtmp_disease_comorbidity_matrix.py/corr_inkscape.png}
    %
    \caption{}
    %
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 2: Length histogram of regions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \begin{figure}[!tbp]
 \centering
 %
 \begin{subfigure}[]{.33\textwidth}
 \textbf{a}
 \\
 \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_hist_100000.png}
 \end{subfigure}
 %
 \begin{subfigure}[]{.33\textwidth}
 \textbf{b}
 \\
 \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_pleiotropic_regions_cumsum.py/pltbar_regions_cumsum.png}
 \end{subfigure}
 %
 \caption{Analysis of pleiotropic regions. \textbf{a}, Length distribution of pleiotropic regions. \textbf{b}, Cumulative sum ordered inversely with the number of GWAS classes.} \label{fig:pleiotropy_region_distribution}
 \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 3: Histograms of variants vs GWAS, eQTL genes and eQTL biosamples
% Fig: Spearman correlation between counts of GWAS categories, eQTL genes and eQTL biosamples
% Fig: VEP consequences
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!ht]
    %
    \centering
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_gwas.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_egene.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_etissue.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_egene_etissue_corr.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/vep.png}
    \end{subfigure}

@@

    \centering
    \begin{subfigure}[]{.49\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_allele_freq.py/eur_af.png}
    \end{subfigure}
    %
    % Fig 9: eQTL gene distance
    \begin{subfigure}[]{.49\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_y_egene_distance.py/violin.png}
    \end{subfigure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 1a-d: Histogram of percentage of explained of GWAS
% Fig 1e: Trait distance matrix
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \begin{subfigure}[]{\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthtmp_disease_comorbidity_matrix.py/corr_inkscape.png}
    \end{subfigure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 2: Length histogram of regions
% Fig 3: Histograms of variants vs GWAS, eQTL genes and eQTL biosamples
% Fig: Spearman correlation between counts of GWAS categories, eQTL genes and eQTL biosamples
% Fig: VEP consequences
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!ht]
    %
    \centering

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_hist_100000.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_pleiotropic_regions_cumsum.py/pltbar_regions_cumsum.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_gwas.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_egene.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_etissue.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{f}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_egene_etissue_corr.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{g}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/vep.png}
    \end{subfigure}

@@

    \centering
    \begin{subfigure}[]{.49\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_allele_freq.py/eur_af.png}
    \end{subfigure}
    %
    % Fig 9: eQTL gene distance
    \begin{subfigure}[]{.49\textwidth}
        \textbf{f}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plt_x_per_variant_y_egene_distance.py/violin.png}
    \end{subfigure}
